Red Oak: Proactive Policy Generation

### 2015-05-09 draft.tex
forwarding decisions

   \subsection*{Forwarding Decision}
   % can give constant decision (e.g. drop() or fwd(loc) to a certain location loc), or decision based on values of the packet (e.g. deliver() which forwards to dst)
   Under the big switch model, the forwarding decisions returned by algorithmic policies are destination-based rather than path-based. For example, the algorithmic policy may decide to deliver a packet, at which point this interpretation will be interpreted as forwarding a packet along a path terminating at the packet's destination. Packets may also be dropped, or forwarding to a static location. Our model also allows for dynamic forwarding based on component of relation, for example to the last seen location of a host according to a MAC-learning controller (not shown in Fig~\ref{fig:range_api}).

>>>>

   \subsection*{Forwarding Decision}
   % can give constant decision (e.g. drop() or fwd(loc) to a certain location loc), or decision based on values of the packet (e.g. deliver() which forwards to dst)
	The programming model for Oak is that each packet entering the network is mapped to a forwarding decision that describes where the packet should end up leaving the network. For simplicity, we assume that we are targeting a one big switch implementation of the network. The one big switch model has been heavily optimized \cite{Obs}, and we view the problem of determining paths through the network as orthogonal to our work here.

   We provide several types of forwarding decisions to the programmer. The programmer can deliver a packet, according to the packet's desination, drop a packet, and forwarding a packet to a static location. Our model also allows for dynamic forwarding based on component of relation, for example to the last seen location of a host according to a MAC-learning controller (not shown in Fig~\ref{fig:range_api}). Finally, the programmer can combine several forwarding decisions into one by using a mulitcast forwarding decision.
